Higher-Order unification for free!

### 2024-04-21 paper/main.tex
reword

\noindent
Opting for this method would result in a suboptimal utilization of the logic
programming engine provided by the ML, as it degrades indexing by
eliminating all data from rule heads. Additionally,
implementing a unification procedure in the ML is likely to be significantly
slower compared to the built-in one.

>>>>

\noindent
This method fails to take advantage of the logic
programming engine provided by the ML, as it degrades indexing by
eliminating all data from rule heads. Additionally,
implementing a unification procedure in the ML is likely to be significantly
slower compared to the built-in one.
